### 2018-05-22 Paper/examples.tex
..

The borehole function is a benchmark reference problem in sensitivity analysis.
It models the discharge of water ($\mathcal{Q}$) through a borehole in terms of
geometrical and physical parameters:
\be
\mathcal{Q} = \frac{\displaystyle
2\pi T_u(H_u - H_l)}{\displaystyle
\ln({r}/{r_w})\Big[1 +
\frac{2LT_u}{
\ln({r}/{r_w})r_w^2K_w} + \frac{T_u}{T_l}\Big]}
\label{eq:bore}
\ee
The radius of influence, $r$ is fixed at 3698.30 m whereas all other parameters
in the right hand side of~\eqref{eq:bore} are considered 
as uncertain. Thus, $\mathcal{Q} = \mathcal{Q}(\vec{\theta})$ with 
\[
   \vec{\theta} = (r_w, L, T_u, H_u, T_l, H_l, K_w)^T.
\] 
Table~\ref{tab:bore} provides distributions of the uncertain inputparameters.

@@

\subsection{Semilinear elliptic PDE with random source term}

We consider the semilinear elliptic PDE,
\begin{equation}\label{equ:semilinear}
\begin{aligned}
-\kappa \Delta u + c u^3 &= q, \quad \text{in } \Omega\\
 u &= 0. \quad \text{on } \partial \Omega
\end{aligned}
\end{equation}
We model the source term as 
\begin{equation}
q(x, y, \theta) = \sum_{i = 1}^N \theta_i \sin(i \pi x)
\cos(i \pi y),
\quad N = 8.
\end{equation}
Here $\kappa \sim U(0.08, 0.12)$, $c \sim U(0.8, 1.2)$, 
and $\theta_i$ are uniformly distributed in interval $[0, 1]$. We consider
the following QoI,
\[
     f(\kappa, c, \theta) = \frac{1}{|D|} \int_D u(x; \kappa, c, \theta) \, dx, 
\]
where $D$ is the region, $[1/2, 3/4] \times [1/2, 3/4]$.

>>>>

The borehole function is a benchmark reference problem in sensitivity analysis.
It models the discharge of water ($\mathcal{Q}$) through a borehole in terms of
geometrical and physical parameters:
\be
\mathcal{Q} = \frac{\displaystyle
2\pi T_u(H_u - H_l)}{\displaystyle
\ln({r}/{r_w})\Big[1 +
\frac{2LT_u}{
\ln({r}/{r_w})r_w^2K_w} + \frac{T_u}{T_l}\Big]}
\label{eq:bore}
\ee
The radius of influence, $r$ is fixed at 3698.30 m whereas all other parameters
in the right hand side of~\eqref{eq:bore} are considered 
as uncertain. Hence, $\mathcal{Q} = \mathcal{Q}(\vec{\theta})$ with 
 $\vec{\theta} = (r_w, L, T_u, H_u, T_l, H_l, K_w)^T$, a vector of
 uncertain parameters. Table~\ref{tab:bore} provides distributions of the
 uncertain input parameters.

@@

\subsection{Semi-linear elliptic PDE with random source term}

We consider the following semi-linear elliptic PDE on a 2D square domain ([0,1]$\times$[0,1]):

\begin{equation}\label{eq:semilinear}
\begin{aligned}
-\kappa \Delta u + c u^3 &= q, \quad \text{in } \Omega\\
 u &= 0. \quad \text{on } \partial \Omega
\end{aligned}
\end{equation}
%
where $u$ is referred to as the velocity, $\kappa$ and $c$ are coefficients of the diffusion term
and the non-linear term in the above equation respectively. The velocity, $u$ is random since the
source term, $q$ in RHS is modelled as a truncated summation with random coefficients:

\be
q = \sum\limits_{i=1}^{N=8}\alpha_i\sin\left(\frac{i\pi x}{8}\right)\cos\left(\frac{i\pi y}{8}\right)
\label{eq:source}
\ee
%
Hence, $u~=~u(\vec{\theta})$ with $\vec{\theta} = (\kappa,c,\alpha_1,\alpha_2,\ldots,\alpha_{8})^T$, a vector
of uncertain parameters. Table~\ref{tab:elliptic} provides distributions of the uncertain
input parameters. The solution of~\eqref{eq:semilinear} for
a particular set of values of the uncertain parameters is illustrated below in Figure~\ref{fig:usoln}.

\begin{table}[htbp]\label{tab:elliptic}
\renewcommand*{\arraystretch}{1.2}
\begin{center}
\begin{tabular}{cl}
\toprule
\textbf{Parameter} & \textbf{Distribution} \\ 
\bottomrule
$\kappa$ & $\mathcal{U}$[0.05,0.1] \\
$c$ & $\mathcal{U}$[1.0,2.0] \\
$\alpha_i$ & $\mathcal{U}$[0.0,4.0] \\
\bottomrule
\end{tabular}
\end{center}
\caption{Description and distributions of uncertain parameters in the 
semi-linear elliptic PDE in~\eqref{eq:semilinear}.}
\end{table}

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.6\textwidth]{./Figures/u_soln}
  \caption{Plotted above is the solution, $u(x,y)$ of~\eqref{eq:semilinear} at fixed values
  of $\kappa$, $c$, and $\alpha_i$ as provided. The color-bar indicates the range of $u$.}
\label{fig:usoln}
\end{center}
\end{figure}

%We consider the semilinear elliptic PDE,
%\begin{equation}\label{equ:semilinear}
%\begin{aligned}
%-\kappa \Delta u + c u^3 &= q, \quad \text{in } \Omega\\
% u &= 0. \quad \text{on } \partial \Omega
%\end{aligned}
%\end{equation}
%We model the source term as 
%\begin{equation}
%q(x, y, \theta) = \sum_{i = 1}^N \theta_i \sin(i \pi x)
%\cos(i \pi y),
%\quad N = 8.
%\end{equation}
%Here $\kappa \sim U(0.08, 0.12)$, $c \sim U(0.8, 1.2)$, 
%and $\theta_i$ are uniformly distributed in interval $[0, 1]$. We consider
%the following QoI,
%\[
%     f(\kappa, c, \theta) = \frac{1}{|D|} \int_D u(x; \kappa, c, \theta) \, dx, 
%\]
%where $D$ is the region, $[1/2, 3/4] \times [1/2, 3/4]$.
